Game Theory Based Peer Grading Mechanisms For MOOCs

### 2015-02-02 Paper.tex
Finally in the right format.

\documentclass{sigchi}

% Use this command to override the default ACM copyright statement (e.g. for preprints). 
% Consult the conference website for the camera-ready copyright statement.

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
% \toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is 	granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\
% {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
% Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
% DOI string from ACM form confirmation}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)

\toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is  granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\
{\emph{L@S'15}}, March 14-15, 2015, Vancouver, Canada. \\
Copyright \copyright~2015 ACM ISBN/15/03...\$15.00. \\
DOI string from ACM form confirmation}

% Arabic page numbers for submission. 
% Remove this line to eliminate page numbers for the camera ready copy
% \pagenumbering{arabic}

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphicx} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs
\usepackage{epstopdf}

% llt: Define a global style for URLs, rather that the default one
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
\makeatother
\urlstyle{leo}

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}

% Make sure hyperref comes last of your loaded packages, 
% to give it a fighting chance of not being over-written, 
% since its job is to redefine many LaTeX commands.
\usepackage[pdftex]{hyperref}
\hypersetup{
pdftitle={Game Theory based Peer Grading Mechanisms for MOOCs},
pdfauthor={LaTeX},
pdfkeywords={MOOC, game theory, mechanism design, peer grading, learning at scale},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}

% create a shortcut to typeset table headings
\newcommand\tabhead[1]{\small\textbf{#1}}

% End of preamble. Here it comes the document.
\begin{document}

\title{Game Theory based Peer Grading Mechanisms for MOOCs}

\numberofauthors{2}
\author{
  \alignauthor William Wu\\
    \affaddr{Acton Boxborough Regional High School}\\
    \affaddr{36 Charter Rd\\ Acton, MA 01720, USA}\\
    \email{willy.vvu@gmail.com}
  \alignauthor Nicolaas Kaashoek\\
    \affaddr{Lexington High School}\\
    \affaddr{251 Waltham Street\\ Lexington, MA 02421, USA}\\
    \email{nick.kaashoek@gmail.com}
}

@@

\keywords{
	Massive Open Online Courses; MOOC; game theory; mechanism design; peer grading; learning at scale;
}

\category{K.3.m.}{Computers and Education}{Miscellaneous}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.9\columnwidth]{Calibration-Flowchart.eps}
\caption{A flowchart of the Calibration Mechanism from the student perspective.}
\label{fig:calibration}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.9\columnwidth]{Error-Calibration-Graph.eps}
\caption{Max error vs Calibrated error}
\label{fig:error-calibration}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=0.9\columnwidth]{Reward-Error-Graph.eps}
\caption{Uncalibrated Error vs Reward}
\label{fig:reward-error}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.9\columnwidth]{Deduction-Flowchart.eps}
\caption{A flowchart of the Deduction Mechanism from the student perspective.}
\label{fig:deduction}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.9\columnwidth]{Comparison-Graph.eps}
\caption{A comparison of mechanisms in terms of effectiveness and scalability.}
\label{fig:comparison}
\end{figure}

@@

\subsection{Additional Authors}
Mentors \newline
\textbf{Matthew~Weinberg}~(\href{mailto:smweinberg@csail.mit.edu}{smweinberg@csail.mit.edu})\newline
\textbf{Christos~Tzamos}~(\href{mailto:ctzamos@gmail.com}{ctzamos@gmail.com})

Advisor \newline
Professor \textbf{Costis~Daskalakis}~(\href{mailto:costis@csail.mit.edu}{costis@csail.mit.edu})

% Note that in a perfect world balance wants to be in the first
% column of the last page.
%
% If balance doesn't work for you, you can remove that and
% hard-code a column break into the bbl file right before you
% submit:
%
% http://stackoverflow.com/questions/2149854/how-to-manually-equalize-columns-
% in-an-ieee-paper-if-using-bibtex
%
% Or, just remove \balance and give up on balancing the last page.
%
\balance

\bibliographystyle{acm-sigchi}
\bibliography{bibliography}
\end{document}

>>>>

\documentclass{chi-ext}
% Please be sure that you have the dependencies (i.e., additional LaTeX packages) to compile this example.
% See http://personales.upv.es/luileito/chiext/

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
% \copyrightinfo{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\
% {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
% Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
% DOI string from ACM form confirmation}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
\copyrightinfo{Permission to make digital or hard copies of part or all of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for third-party components of this work must be honored. For all other uses, contact the Owner/Author. \\
Copyright is held by the owner/author(s). \\
{\emph{L@S 2015}}, Mar 14-18, 2015, Vancouver, BC, Canada \\
ACM 978-1-4503-3411-2/15/03. \\
http://dx.doi.org/10.1145/2724660.2728676}

\title{Game Theory Based Peer Grading Mechanisms For MOOCs}

\numberofauthors{5}
% Notice how author names are alternately typesetted to appear ordered in 2-column format;
% i.e., the first 4 autors on the first column and the other 4 auhors on the second column.
% Actually, it's up to you to strictly adhere to this author notation.
\author{
  \alignauthor{
    \textbf{Constantinos Daskalakis}\\
    \affaddr{Massachusetts Institute of Technology}\\
    \affaddr{77 Massachusetts Avenu}\\
    \affaddr{Cambridge, MA 02139}\\
    \email{costis@csail.mit.edu}
  }\alignauthor{
    \textbf{Nicolaas Kaashoek}\\
    \affaddr{Lexington High School}\\
    \affaddr{251 Waltham Street}\\
    \affaddr{Lexington, MA 02421, USA}\\
    \email{nick.kaashoek@gmail.com}
  }
  \vfil
  \alignauthor{
    \textbf{Christos Tzamos}\\
    \affaddr{Massachusetts Institute of Technology}\\
    \affaddr{77 Massachusetts Avenu}\\
    \affaddr{Cambridge, MA 02139}\\
    \email{ctzamos@gmail.com}
  }\alignauthor{
    \textbf{Matthew Weinberg}\\
    \affaddr{Massachusetts Institute of Technology}\\
    \affaddr{77 Massachusetts Avenu}\\
    \affaddr{Cambridge, MA 02139}\\
    \email{smweinberg@csail.mit.edu}
  }
  \vfil
  \alignauthor{
    \textbf{William Wu}\\
    \affaddr{Acton Boxborough Regional High School}\\
    \affaddr{36 Charter Rd}\\
    \affaddr{Acton, MA 01720, USA}\\
    \email{willy.vvu@gmail.com}
  }
}

% Paper metadata (use plain text, for PDF inclusion and later re-using, if desired)
\def\plaintitle{Game Theory based Peer Grading Mechanisms for MOOCs}
\def\plainauthor{William Wu}
\def\plainkeywords{MOOC, game theory, mechanism design, peer grading, learning at scale}
\def\plaingeneralterms{Game Theory, Mechanism Design, Peer Grading}

\hypersetup{
  % Your metadata go here
  pdftitle={\plaintitle},
  pdfauthor={\plainauthor},  
  pdfkeywords={\plainkeywords},
  pdfsubject={\plaingeneralterms},
  % Quick access to color overriding:
  %citecolor=black,
  %linkcolor=black,
  %menucolor=black,
  %urlcolor=black,
}

\usepackage{graphicx}   % for EPS use the graphics package instead
\usepackage{balance}    % useful for balancing the last columns
\usepackage{bibspacing} % save vertical space in references

\usepackage{epstopdf}

\begin{document}

@@

\keywords{Massive Open Online Courses; MOOC; game theory; mechanism design; peer grading; learning at scale;}

\category{H.5.m}{Information interfaces and presentation (e.g., HCI)}{Miscellaneous}. 
%See \cite{ACMCCS} 
See: \url{http://www.acm.org/about/class/1998/} 
for help using the ACM Classification system.

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{Calibration-Flowchart.eps}
  \caption{A flowchart of the Calibration Mechanism from the student perspective.}
  \label{fig:calibration}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{Error-Calibration-Graph.eps}
  \caption{Max error vs Calibrated error}
  \label{fig:error-calibration}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{Reward-Error-Graph.eps}
  \caption{Uncalibrated Error vs Reward}
  \label{fig:reward-error}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{Deduction-Flowchart.eps}
  \caption{A flowchart of the Deduction Mechanism from the student perspective.}
  \label{fig:deduction}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{Comparison-Graph.eps}
  \caption{A comparison of mechanisms in terms of effectiveness and scalability.}
  \label{fig:comparison}
\end{figure}

@@

\balance
\bibliographystyle{acm-sigchi}
\bibliography{bibliography}

\end{document}
